Quantile Regressions via Method of Moments with multiple fixed effects

### 2023-11-04 article/article.qmd
Update article.qmd

$$\begin{aligned}
\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
\end{aligned}
$$

@@

- `mmqreg` in Stata: `net install mmqre, from(https://friosavila.github.io/stpackages)
- `mmqreg` in R: Program Available in mmqreg repository in GitHub (https://github.com/friosavila/mmqreg)
- `mmqreg` in Python: 
- `mmqreg` in julia:

>>>>

$$\begin{aligned}
\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \psi_{i} \psi_{j}
\end{aligned}
$$

@@

- `mmqreg` in Stata: `net install mmqreg, from(https://friosavila.github.io/stpackages)
- `mmqreg` in R: Program Available in mmqreg repository in GitHub (https://github.com/friosavila/mmqreg)
- `mmqreg` in Python: 
- `mmqreg` in julia:
